% ============================================================
% referencias.tex — Bibliografía
% ============================================================

\section{Referencias}

\begin{thebibliography}{99}

\bibitem{hochreiter1997}
Hochreiter, S. \& Schmidhuber, J. (1997).
Long Short-Term Memory.
\textit{Neural Computation}, 9(8), 1735--1780.

\bibitem{cho2014}
Cho, K., van Merriënboer, B., Gulcehre, C., Bahdanau, D., Bougares, F., Schwenk, H. \& Bengio, Y. (2014).
Learning Phrase Representations using RNN Encoder-Decoder for Statistical Machine Translation.
\textit{Proceedings of the 2014 Conference on Empirical Methods in Natural Language Processing (EMNLP)}, 1724--1734.

\bibitem{jozefowicz2015}
Jozefowicz, R., Zaremba, W. \& Sutskever, I. (2015).
An Empirical Exploration of Recurrent Network Architectures.
\textit{Proceedings of the 32nd International Conference on Machine Learning (ICML)}, 2342--2350.

\bibitem{kingma2015}
Kingma, D. P. \& Ba, J. (2015).
Adam: A Method for Stochastic Optimization.
\textit{Proceedings of the 3rd International Conference on Learning Representations (ICLR)}.

\bibitem{maas2011}
Maas, A. L., Daly, R. E., Pham, P. T., Huang, D., Ng, A. Y. \& Potts, C. (2011).
Learning Word Vectors for Sentiment Analysis.
\textit{Proceedings of the 49th Annual Meeting of the Association for Computational Linguistics (ACL)}, 142--150.

\bibitem{srivastava2014}
Srivastava, N., Hinton, G., Krizhevsky, A., Sutskever, I. \& Salakhutdinov, R. (2014).
Dropout: A Simple Way to Prevent Neural Networks from Overfitting.
\textit{Journal of Machine Learning Research}, 15(56), 1929--1958.

\end{thebibliography}
